Fourmile Calibrations and Output

### 2024-07-16 fourmile_outputs_2013edits.Rmd
minor update

# Join param & RD/RG

join <- gw_maxcumsum %>%
  rename(input_data = source)

params1 <- params %>%
  dplyr::select(-input_data) %>%
  rename(input_data = cal) %>%
  dplyr::select(-c(year_missing))

#
params_weighted1 <- params_weighted %>%
  mutate(input_data = paste(source, year_missing, sep = "_")) %>% 
  pivot_wider(names_from = 'param',
              values_from = 'area_weighted_average') %>%
  rename_with(~ paste0(., '_weighted'), 4:9) %>%
  dplyr::select(-c(year_missing, source))

join <- left_join(join, params1, by = c('input_data')) %>%
  pivot_wider(., names_from='param', values_from='value') %>%
  pivot_wider(., names_from = 'flow_type', values_from = 'flow_cms')

join <- left_join(join, params_weighted1, by = 'input_data')

write_csv(join, '/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/flow_params.csv')

>>>>

<!-- # Join param & RD/RG -->

<!-- ```{r} -->

<!-- join <- gw_maxcumsum %>% -->
<!--   rename(input_data = source) -->

<!-- params1 <- params %>% -->
<!--   dplyr::select(-input_data) %>% -->
<!--   rename(input_data = cal) %>% -->
<!--   dplyr::select(-c(year_missing)) -->

<!-- # -->
<!-- params_weighted1 <- params_weighted %>% -->
<!--   mutate(input_data = paste(source, year_missing, sep = "_")) %>%  -->
<!--   pivot_wider(names_from = 'param', -->
<!--               values_from = 'area_weighted_average') %>% -->
<!--   rename_with(~ paste0(., '_weighted'), 4:9) %>% -->
<!--   dplyr::select(-c(year_missing, source)) -->

<!-- join <- left_join(join, params1, by = c('input_data')) %>% -->
<!--   pivot_wider(., names_from='param', values_from='value') %>% -->
<!--   pivot_wider(., names_from = 'flow_type', values_from = 'flow_cms') -->

<!-- join <- left_join(join, params_weighted1, by = 'input_data') -->

<!-- write_csv(join, '/Users/megansears/Documents/Repos/fourmile/38HRU_sept2013_updates/flow_params.csv') -->
